 

\section{How get $x' = A_{1x}x +A_{1zs}Z_{s} + A_{1ns}Z_{ns}+A_{1s}$?}
To get this system, a good set of unknowns must be done. Only the necessary unknowns are added. The
following examples show how this choice could be done.
\input{example1.tex}
\input{example2.tex}
\input{example3.tex}
\input{example4.tex}
\input{example5.tex}

\subsection{conclusion}
The vector x contains inductor's currents and capacitor's tensions. Derivate inductor's current is equal to a
nodal voltage difference.\\
About the capacitor's tensions, we use the Minimum Spanning Tree of the capacitor' tension to avoid cycle.\\


\begin{algorithm}
\caption{fill the matrices : $x'=A_{1x}x+A_{1s}Z_{s}+A_{1ns}Z_{ns}$ }
\begin{algorithmic}
\REQUIRE Init\_I\_in\_x : initialize internal data structure to get all I from x.
\REQUIRE Next\_I\_in\_x : return the next available I from x. If there are not available x, return 0.\\
\REQUIRE Minimum Spanning Tree of the capacitor' tension graph
\REQUIRE Init\_MST : initialize internal data structure to get all u from x.
\REQUIRE Next\_u\_in\_MST : return a available U's neighbour from MST if possible. If there are not
available u in MST, return 0.\\
\REQUIRE Next\_U\_in\_x : return the next available U from x. If there are not available x, return 0.\\

0\\
\COMMENT{About current}\\
\COMMENT{get first current}
\STATE Init\_I\_in\_x()
\STATE $I_{kj}$ = Next\_I\_in\_x()
\WHILE{$I_{kj}$}
\STATE use $LI'=V_{j}-V_{k}$ to fill $I_{kj}$'s line.
\ENDWHILE\\
\COMMENT{About tension}\\
\COMMENT{get a first capacitor tension}
\STATE Init\_MST()
\STATE $U_{kj}$ = Next\_u\_in\_MST()
\WHILE{$U_{kj}$}
\STATE l=j or k with KCL(k) available.
\STATE Use CU'=I and KCL(k) to fill $U_{ki}$'s line.\\
\STATE enable KCL(k)

\STATE $U_{kj}$= Next\_u\_in\_MST ()
\ENDWHILE
\STATE $U_{kj}$ = Next\_U\_in\_x()
\WHILE {$U_{kj}$}
\STATE Add an unknown $I_{kj}$, and use it to fill the matrices. Write I=CU'.
\STATE $U_{kj}$ = Next\_U\_in\_x()
\ENDWHILE
\COMMENT{reverse A : $Ax'=Bx+CZ_{s}+DZ_{ns}$\\}
\STATE $A^{-1}$=Inv(A)
\STATE $x'=A_{1x}x+A_{1s}Z_{s}+A_{1ns}Z_{ns}$
\end{algorithmic}
\end{algorithm}

