\section{The linear non smooth components}
\subsection{Topology. Choice of smooth and nonsmooth components.}
The stamp method is used for the linear components. About the non smooth components, a piecewise
linear modeling describes the component's behavior. This geometry is written with linear
complementarity conditions. 
\subsection{Unknowns}
Before go head, the unknowns vector X is subdivided:
\begin{enumerate}
\item[--] x contains only the dynamic unknowns(currents in inductor and tensions from capacitor branches)
\item[--] $Z_{s}$ contains only the non dynamic unknowns(Voltage nodes,... ).
\item[--] $Z_{ns}$ contains the useful currents and tensions for the non smooth components.
\end{enumerate}
\subsection{Linear local formulation}
For each non smooth component, we assume that the behavior can be written as the following the mixed linear  complementarity condition, that is:
\begin{equation}\left(\begin{array}{c}
\beta = Z_{nsi} = A_{i}x+B_{i}\lambda_{i}+C_{i}Z_{s} + a_{i}\\
y_{i}=D_{i}x+E_{i}Z_{s}+F_{i}\lambda_{i}+G_{i}Z_{nsi}+e_{i}\\
0 \leq y_{i} \, \perp \, \lambda_{i} \geq 0
\end{array}\right)
\end{equation}
where $Z_{nsi}$ is a voltage and currents vector. $a_{i},e_{i},\lambda_{i}$ and $y_{i}$ are some constants vectors which characterizes the components. At the end
of this document, we will see how ideal diode and piecewise linear models of transistor fits into this formulation.


\subsection{Example of a linear global formulation}
It consists in writing all the complementary conditions in the equations of the MNA. An example with 5 non smooth components is given by:

\[\left(\begin{array}{c}
  Z_{ns}\\
  \hline
  Z_{ns1} \\
  Z_{ns2} \\
  Z_{ns3} \\
  Z_{ns4} \\
  Z_{ns5} \\
\end{array}\right) =
\left(\begin{array}{c}
  C_{1x}\\
  \hline
  A1\\
  A2\\
  A3\\
  A4\\
  A5\\
\end{array}\right)*x +
\left(\begin{array}{c}
  C_{1s}\\
  \hline
  C1\\
  C2\\
  C3\\
  C4\\
  C5\\
\end{array}\right)*Z_{s} +
\left(\begin{array}{ccccc}
  C1_{\lambda}\\
  \hline
  B1&0&0&0&0\\
  0&B2&0&0&0\\
  0&0&B3&0&0\\
  0&0&0&B4&0\\
  0&0&0&0&B5\\
\end{array}\right)*
\left(\begin{array}{c}
  \lambda\\
  \hline
  \lambda _{1} \\
  \lambda _{2}\\
  \lambda _{3}\\
  \lambda _{4}\\
  \lambda _{5}\\
\end{array}\right)+
\left(\begin{array}{c}
  cst\\
  \hline
   cst_{1} \\
   cst_{2}\\
   cst_{3}\\
   cst_{4}\\
   cst_{5}\\
\end{array}\right)
\]

\[\left(\begin{array}{c}
  Y\\
  \hline
   Y_{1} \\
   Y_{2} \\
   Y_{3} \\
   Y_{4} \\
   Y_{5} \\
\end{array}\right) =
\left(\begin{array}{c}
  D_{1x}\\
  \hline
  D1\\
  D2\\
  D3\\
  D4\\
  D5\\
\end{array}\right)*x +
\left(\begin{array}{c}
  D_{1s}\\
  \hline
  E1\\
  E2\\
  E3\\
  E4\\
  E5\\
\end{array}\right)*Z_{s} +
\left(\begin{array}{ccccc}
  D1_{\lambda}\\
  \hline
  F1&0&0&0&0\\
  0&F2&0&0&0\\
  0&0&F3&0&0\\
  0&0&0&F4&0\\
  0&0&0&0&F5\\
\end{array}\right)*
\left(\begin{array}{c}
  \lambda\\
  \hline
   \lambda _{1} \\
   \lambda _{2}\\
   \lambda _{3}\\
   \lambda _{4}\\
   \lambda _{5}\\
\end{array}\right)+\]
\[
\left(\begin{array}{ccccc}
  D1_{ns}\\
  \hline
  G1&0&0&0&0\\
  0&G2&0&0&0\\
  0&0&G3&0&0\\
  0&0&0&G4&0\\
  0&0&0&0&G5\\
\end{array}\right)*
\left(\begin{array}{c}
  Zns\\
  \hline
   Z_{ns1} \\
   Z_{ns2}\\
   Z_{ns3}\\
   Z_{ns4}\\
   Z_{ns5}\
\end{array}\right)+
\left(\begin{array}{c}
  cst\\
  \hline
   cst_{1} \\
   cst_{2}\\
   cst_{3}\\
   cst_{4}\\
   cst_{5}\\
\end{array}\right)
\]
Finally, the global formulation form is : 

\[\left(\begin{array}{c}
Z_{ns}= C_{1x}x+C_{1zs}Z_{s}+C_{1\lambda}\lambda +C_{1s}\\
Y=D_{1x}x +D_{1zs}Z_{s}+D_{1ns}Z_{ns}+D_{1\lambda}\lambda+D_{1s}\\
0 \leq Y \, \perp \, \lambda \geq 0
\end{array}\right)\]
\newpage
\section{Extended MNA for nonsmooth linear components}
This part describes the automatic formulation into a Mixed Linear Complementarity System (MLCS) of a circuit. It consists in adapting the MNA to manage non-smooth model.

\subsection{MLCS and MLCP definitions}
\begin{definition}\index{Complementarity problem ! mixed linear} \index{MLCP}
  Given the matrices  ${A} \in \RR^{n \times n}$, ${B} \in \RR^{m \times m}$, ${C} \in \RR^{n \times m}$, ${D} \in \RR^{m \times n}$, and the vectors  $ {a} \in \RR^n, {b} \in \RR^m$, the MLCP denoted by $\mathrm{MLCP}(A,B,C,D,a,b)$ consists in finding two vectors $ {u} \in \RR^n$ and  $ {v} \in \RR^m$ such that
\begin{equation}\label{eq:mlcp1} 
  \begin{cases}
    A u + C v + a =0 \\  \\
    {0} \le {v} \perp     Du +B v +b   \ge {0}
  \end{cases}.
\end{equation}
The  MLCP can be defined equivalently in the following form denoted by $\mathrm{MLCP}(M,q,\mathcal E,\mathcal I)$
\begin{equation}
  \label{eq:mlcp2}
  \begin{cases}
    w = M z +q \\
    w_i=0,\forall  i \in \mathcal E \\
    {0} \le z_i \perp w_i \ge {0}, \forall  i \in \mathcal I 
 \end{cases}
\end{equation}
where  $\mathcal E$ and $\mathcal I$ are finite sets of indices such that $\mathrm{card}(\mathcal E \cup \mathcal I  ) = n$ and $\mathcal E \cap \mathcal I  = \emptyset$.\end{definition}
The MLCP is a mixture between an LCP and a system of linear equations. The former definition~(\ref{eq:mlcp1}) can be casted into the second one~(\ref{eq:mlcp2}) by introducing
\begin{equation}
  \label{eq:mlcp-m}
  M = \left[
  \begin{array}{cc}
   A & C \\
   D & B
  \end{array}\right],\quad   q = \left[
  \begin{array}{c}
    a \\
    b
  \end{array}\right],\quad   z = \left[
  \begin{array}{c}
    u \\
    v
  \end{array}\right],\quad   w = \left[
  \begin{array}{c}
    0\\
    w_i, \forall  i \in \mathcal I 
  \end{array}\right]
\end{equation}




Equivalently, the MLCS can be defined by an implicit system

\begin{definition}\index{Complementarity system ! mixed linear} \index{MLCS}
  Given the matrices  ${M} \in \RR^{n \times n}$, ${A} \in \RR^{n \times n}$, ${B} \in \RR^{m \times
  m}$, ${C} \in \RR^{n \times m}$, ${D} \in \RR^{m \times n}$, and the vectors  $ {a} \in \RR^n, {b}
  \in \RR^m$, the implicit MLCS denoted by $\mathrm{IMLCS}(M,A,B,C,D,a,b)$ consists in finding two vectors $ {x} \in \RR^n$ and  $ {v} \in \RR^m$ such that
\begin{equation}\label{eq:mlcs1} 
  \begin{cases}
   M x' = A x + C v + a  \\  \\
   {0} \le {v} \perp     Dx +B v +b   \ge {0}
  \end{cases}.
\end{equation}
\end{definition}

or an explicit system
\begin{definition}\index{Complementarity system ! mixed linear} \index{MLCS}
  Given the matrices   ${A_{x}} \in \RR^{n \times n}$, ${A_{z}} \in \RR^{n \times
  p}$, ${A_{v}} \in \RR^{n \times m}$, ${B_{x}} \in \RR^{p \times n}$, ${B_{z}} \in \RR^{p \times
  p}$, ${B_{v}} \in \RR^{p \times m}$, ${C_{x}} \in \RR^{m \times n}$, ${C_{z}} \in \RR^{m \times p}$,${C_{v}} \in \RR^{m \times m}$, and
  the vectors  $ {a} \in \RR^n$,$ {b}  \in \RR^p$,$ {c}  \in \RR^m$, the explicit MLCS denoted by
  $\mathrm{EMLCS}(A_{x},A_{z},A_{v},B_{x},B_{z},B_{v},C_{x},C_{z},C_{v},a,b,c)$ consists in finding three vectors $ {x}
  \in \RR^n$, $ {z} \in \RR^p$ and  $ {v} \in \RR^m$ such that
\begin{equation}\label{eq:mlcs2} 
  \begin{cases}
   x' = A_{x} x +A_{z} z +A_{v} v + a  \\
   0 = B_{x} x +B_{z} z + B_{v} v +b \\ \\
   {0} \le {v} \perp     C_{x} x+ C_{z}z +C_{v} v +c   \ge {0}
  \end{cases}.
\end{equation}
\end{definition}
\subsection{Hypothesis}
The MNA assumes smooth branches are explicit functions of current or voltage. It means each smooth
branch is Voltage Defined (V.D.) or Current Defined (C.D.)\\

With the same assumption, all branches can be divided into following classes:\\
\begin{enumerate}
\item The  \underline{C.D. branches} 
\item The  \underline{V.D. branches}
 \item The  \underline{non smooth branches}
 \item The \underline{dynamical capacitor branches}
 \item The \underline{dynamical inductors branches}
\end{enumerate}




\subsection{Nonsmooth equations and MLCS}
With the linear complementary condition, the system becomes an explicit MLCS of the form :
\[x' = A_{1x}x +A_{1zs}Z_{s} + A_{1ns}Z_{ns}+A_{1s}\]
\[0  = B_{1x}x+B_{1zs}Z_{s} + B_{1ns}Z_{ns}+B_{1s}\]
\[Z_{ns}= C_{1x}x+C_{1zs}Z_{s}+C_{1\lambda}\lambda +C_{1s}\]
\[Y=D_{1x}x +D_{1zs}Z_{s}+D_{1ns}Z_{ns}+D_{1\lambda}\lambda+D_{1s}\]
\[0 \leq Y \, \perp \, \lambda \geq 0\]
\input{DAE_FORM.tex}
\newpage

\section{Summary of  the Matrix formulation}

The previous section describes how get the following system:
\[\left(\begin{array}{c}
x'=A_{1x}x +A_{1zs}Z_{s} + A_{1ns}Z_{ns}+A_{1s}\\
0=B_{1x}x+B_{1zs}Z_{s} + B_{1ns}Z_{ns}+B_{1s}\\
Z_{ns}= C_{1x}x+C_{1zs}Z_{s}+C_{1\lambda}\lambda +C_{1s}\\
Y=D_{1x}x +D_{1zs}Z_{s}+D_{1ns}Z_{ns}+D_{1\lambda}\lambda+D_{1s}\\
0 \leq Y \, \perp \, \lambda \geq 0
\end{array}\right)\]
Substitute $Z_{ns}$:
\[\left(\begin{array}{c}
R=A_{1ns}C_{1\lambda}\\
x'=(A_{1x}+A_{1ns}C_{1x})x +(A_{1zs}+A_{1ns}C_{1zs})Z_{s} +R\lambda+A_{1s} + A_{1ns}C_{1s}\\
x'=A_{2x}x +A_{2zs}Z_{s} +R \lambda +A_{2s}\\
0=(B_{1x}+B_{1ns}C_{1x})x+(B_{1zs}+B_{1ns}C_{1s})Z_{s} + B_{1ns}C_{1\lambda}\lambda +B_{1s} + B_{1ns}C_{1s} \\
0=B_{2x}x+B_{2zs}Z_{s} + B_{2\lambda}\lambda + B_{2s}\\
Y=(D_{1x}+D_{1ns}C_{1x})x+(D_{1zs}+D_{1ns}C_{1s})Z_{s}+(D_{1\lambda}+D_{1ns}C_{1\lambda})\lambda +D_{1s}+D_{1ns}C_{1s}\\
Y=D_{2x}x+D_{2zs}Z_{s}+D_{2\lambda}\lambda + D_{2s} \\
0 \leq Y \, \perp \, \lambda \geq 0\\
\end{array}\right)\]
$A_{2s}, B_{2s}$ and $D_{2s}$ are vectors.



%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "ace"
%%% End: 
