


\section{The linear non smooth components}
\subsection{Topology. Choice of smooth and nonsmooth components.}
\textcolor{red}{\tt TBW}
\subsection{Unknowns}
Before go head, the unknowns vector X is subdivided:
\begin{enumerate}
\item[--] x contains only the dynamic unknowns(currents in inductor and tensions from capacitor branches)
\item[--] $Z_{s}$ contains only the non dynamic unknowns(Voltage nodes,... ).
\item[--] $Z_{ns}$ contains the useful currents and tensions for the non smooth components.
\end{enumerate}
\subsection{Linear local formulation}
For each non smooth component, we assume that the behavior can be written as the following the mixed linear  complementarity condition, that is:
\begin{equation}\left(\begin{array}{c}
\beta = zns_{i} = A_{i}x+B_{i}\lambda_{i}+C_{i}z_{s} + a_{i}\\
y_{i}=D_{i}x+E_{i}z_{s}+F_{i}\lambda_{i}+G_{i}zns_{i}+e_{i}\\
0 \leq y_{i} \, \perp \, \lambda_{i} \geq 0
\end{array}\right)
\end{equation}
where $zns_{i}$ is a voltage and currents vector\textcolor{red}{\tt notation $zns$?}. $a_{i},e_{i},\lambda_{i}$ and $y_{i}$ are some constants vectors which characterizes the components. At the end
of this document, we will see how ideal diode and piecewise linear models of transistor fits into this formulation.


\subsection{Example of a linear global formulation}
It consists in writing all the complementary conditions in the equations of the MNA. An example with 5 non smooth components is given by:

\[\left(\begin{array}{c}
  Z_{ns}\\
  \hline
  Z_{ns1} \\
  Z_{ns2} \\
  Z_{ns3} \\
  Z_{ns4} \\
  Z_{ns5} \\
\end{array}\right) =
\left(\begin{array}{c}
  C_{1x}\\
  \hline
  A1\\
  A2\\
  A3\\
  A4\\
  A5\\
\end{array}\right)*x +
\left(\begin{array}{c}
  C_{1s}\\
  \hline
  C1\\
  C2\\
  C3\\
  C4\\
  C5\\
\end{array}\right)*Z_{s} +
\left(\begin{array}{ccccc}
  C1_{\lambda}\\
  \hline
  B1&0&0&0&0\\
  0&B2&0&0&0\\
  0&0&B3&0&0\\
  0&0&0&B4&0\\
  0&0&0&0&B5\\
\end{array}\right)*
\left(\begin{array}{c}
  \lambda\\
  \hline
  \lambda _{1} \\
  \lambda _{2}\\
  \lambda _{3}\\
  \lambda _{4}\\
  \lambda _{5}\\
\end{array}\right)+
\left(\begin{array}{c}
  cst\\
  \hline
   cst_{1} \\
   cst_{2}\\
   cst_{3}\\
   cst_{4}\\
   cst_{5}\\
\end{array}\right)
\]

\[\left(\begin{array}{c}
  Y\\
  \hline
   Y_{1} \\
   Y_{2} \\
   Y_{3} \\
   Y_{4} \\
   Y_{5} \\
\end{array}\right) =
\left(\begin{array}{c}
  D_{1x}\\
  \hline
  D1\\
  D2\\
  D3\\
  D4\\
  D5\\
\end{array}\right)*x +
\left(\begin{array}{c}
  D_{1s}\\
  \hline
  E1\\
  E2\\
  E3\\
  E4\\
  E5\\
\end{array}\right)*Z_{s} +
\left(\begin{array}{ccccc}
  D1_{\lambda}\\
  \hline
  F1&0&0&0&0\\
  0&F2&0&0&0\\
  0&0&F3&0&0\\
  0&0&0&F4&0\\
  0&0&0&0&F5\\
\end{array}\right)*
\left(\begin{array}{c}
  \lambda\\
  \hline
   \lambda _{1} \\
   \lambda _{2}\\
   \lambda _{3}\\
   \lambda _{4}\\
   \lambda _{5}\\
\end{array}\right)+\]
\[
\left(\begin{array}{ccccc}
  D1_{ns}\\
  \hline
  G1&0&0&0&0\\
  0&G2&0&0&0\\
  0&0&G3&0&0\\
  0&0&0&G4&0\\
  0&0&0&0&G5\\
\end{array}\right)*
\left(\begin{array}{c}
  Zns\\
  \hline
   zns_{1} \\
   zns_{2}\\
   zns_{3}\\
   zns_{4}\\
   zns_{5}\
\end{array}\right)+
\left(\begin{array}{c}
  cst\\
  \hline
   cst_{1} \\
   cst_{2}\\
   cst_{3}\\
   cst_{4}\\
   cst_{5}\\
\end{array}\right)
\]
Finally, the global formulation form is : 

\[\left(\begin{array}{c}
Z_{ns}= C_{1x}x+C_{1zs}Z_{s}+C_{1\lambda}\lambda +C_{1s}\\
Y=D_{1x}x +D_{1zs}Z_{s}+D_{1ns}Z_{ns}+D_{1\lambda}\lambda+D_{1s}\\
0 \leq Y \, \perp \, \lambda \geq 0
\end{array}\right)\]
\newpage
\section{Extended MNA for nonsmooth linear components}
This part describes the automatic formulation into a Mixed Linear Complementarity System (MLCS) of a circuit. It consists in adapting the MNA to manage non-smooth model.

\subsection{MLCS and MLCP definitions}
\begin{definition}\index{Complementarity problem ! mixed linear} \index{MLCP}
  Given the matrices  ${A} \in \RR^{n \times n}$, ${B} \in \RR^{m \times m}$, ${C} \in \RR^{n \times m}$, ${D} \in \RR^{m \times n}$, and the vectors  $ {a} \in \RR^n, {b} \in \RR^m$, the MLCP denoted by $\mathrm{MLCP}(A,B,C,D,a,b)$ consists in finding two vectors $ {u} \in \RR^n$ and  $ {v} \in \RR^m$ such that
\begin{equation}\label{eq:mlcp1} 
  \begin{cases}
    A u + C v + a =0 \\  \\
    {0} \le {v} \perp     Du +B v +b   \ge {0}
  \end{cases}.
\end{equation}
The  MLCP can be defined equivalently in the following form denoted by $\mathrm{MLCP}(M,q,\mathcal E,\mathcal I)$
\begin{equation}
  \label{eq:mlcp2}
  \begin{cases}
    w = M z +q \\
    w_i=0,\forall  i \in \mathcal E \\
    {0} \le z_i \perp w_i \ge {0}, \forall  i \in \mathcal I 
 \end{cases}
\end{equation}
where  $\mathcal E$ and $\mathcal I$ are finite sets of indices such that $\mathrm{card}(\mathcal E \cup \mathcal I  ) = n$ and $\mathcal E \cap \mathcal I  = \emptyset$.\end{definition}
The MLCP is a mixture between an LCP and a system of linear equations. The former definition~(\ref{eq:mlcp1}) can be casted into the second one~(\ref{eq:mlcp2}) by introducing
\begin{equation}
  \label{eq:mlcp-m}
  M = \left[
  \begin{array}{cc}
   A & C \\
   D & B
  \end{array}\right],\quad   q = \left[
  \begin{array}{c}
    a \\
    b
  \end{array}\right],\quad   z = \left[
  \begin{array}{c}
    u \\
    v
  \end{array}\right],\quad   w = \left[
  \begin{array}{c}
    0\\
    w_i, \forall  i \in \mathcal I 
  \end{array}\right]
\end{equation}




Equivalently, the MLCS can be defined by 

\begin{definition}\index{Complementarity system ! mixed linear} \index{MLCS}
  Given the matrices  ${A} \in \RR^{n \times n}$, ${B} \in \RR^{m \times m}$, ${C} \in \RR^{n \times m}$, ${D} \in \RR^{m \times n}$, and the vectors  $ {a} \in \RR^n, {b} \in \RR^m$, the MLCP denoted by $\mathrm{MLCP}(A,B,C,D,a,b)$ consists in finding two vectors $ {u} \in \RR^n$ and  $ {v} \in \RR^m$ such that
\begin{equation}\label{eq:mlcp1} 
  \begin{cases}
   x' = A x + C v + a =0 \\  \\
   {0} \le {v} \perp     Dx +B v +b   \ge {0}
  \end{cases}.
\end{equation}
\end{definition}

\textcolor{red}{\tt Is it sufficient ??}
\subsection{Hypothesis}
The MNA assumes smooth branches are explicit functions of current or voltage. It means each smooth
branch is Voltage Defined (V.D.) or Current Defined (C.D.)\\

With the same assumption, all branches can be divided into following classes:\\
\begin{enumerate}
\item The  \underline{C.D. branches} 
\item The  \underline{V.D. branches}
 \item The  \underline{non smooth branches}
 \item The \underline{dynamical capacitor branches}
 \item The \underline{dynamical inductors branches}
\end{enumerate}



\subsection{Smooth equations and the DAE system.}
It is the same physical equations than in the MNA. This part describes the form and the unknowns
used in our formulation.

\begin{enumerate} 
 \item If a node is not connected to a capacitor then the Kirchhoff Current Law (KCL) is static. \\
  \item The V.D. equation (VDE) : \\
    A V.D. branch give an equation :
    \[V_{i}-V_{j} = \sum_{i}^{}a_{i}V_{i} + \sum_{j\in J}^{}b_{j}I_{j} +   source\]
    This equation comes from the branch constitution, not from the Kirchhoff Law. (ex : U = R*I)
  \item If a node is connected to a capacitor then the Kirchhoff Current Law is dynamic (KCL).\\
    NB : The current in the capacitor branches is written with :
    \[I = C*\frac{d(V_{i} - V_{j})}{dt}\]
  \item The inductor law (IL) : 
     \[V_{i} - V_{j} = L*\frac{dI}{dt}\]
\end{enumerate}

These equations lead to a DAE of the form:
\[MX'+NX=s(t)\]
In general cases, the matrix $M$ is singular. But, with a good choice of the set of unknowns, it is possible to write a DAE of the form :
\[x' = A_{1x}x +A_{1zs}Z_{s} + A_{1ns}Z_{ns}+A_{1s}\]
\[0  = B_{1x}x+B_{1zs}Z_{s} + B_{1ns}Z_{ns}+B_{1s}\]

\textcolor{red}{\tt Without $Z_{ns}$ ??}
\subsection{Nonsmooth equations ad MLCP}
\textcolor{red}{\tt TBW}
\input{DAE_FORM.tex}
\newpage
\section{Summary of  the Matrix formulation}

The previous section describes how get the following system:
\[\left(\begin{array}{c}
x'=A_{1x}x +A_{1zs}Z_{s} + A_{1ns}Z_{ns}+A_{1s}\\
0=B_{1x}x+B_{1zs}Z_{s} + B_{1ns}Z_{ns}+B_{1s}\\
Z_{ns}= C_{1x}x+C_{1zs}Z_{s}+C_{1\lambda}\lambda +C_{1s}\\
Y=D_{1x}x +D_{1zs}Z_{s}+D_{1ns}Z_{ns}+D_{1\lambda}\lambda+D_{1s}\\
0 \leq Y \, \perp \, \lambda \geq 0
\end{array}\right)\]
Substitute $Z_{ns}$:
\[\left(\begin{array}{cc}
R=A_{1ns}C_{1\lambda}&(eq1)\\
x'=(A_{1x}+A_{1ns}C_{1x})x +(A_{1zs}+A_{1ns}C_{1zs})Z_{s} +R\lambda+A_{1s} + A_{1ns}C_{1s}\\
x'=A_{2x}x +A_{2zs}Z_{s} +R \lambda +A_{2s}&(eq2)\\
0=(B_{1x}+B_{1ns}C_{1x})x+(B_{1zs}+B_{1ns}C_{1s})Z_{s} + B_{1ns}C_{1\lambda}\lambda +B_{1s} + B_{1ns}C_{1s} \\
0=B_{2x}x+B_{2zs}Z_{s} + B_{2\lambda}\lambda + B_{2s}&(eq3)\\
Y=(D_{1x}+D_{1ns}C_{1x})x+(D_{1zs}+D_{1ns}C_{1s})Z_{s}+(D_{1\lambda}+D_{1ns}C_{1\lambda})\lambda +D_{1s}+D_{1ns}C_{1s}=\\
Y=D_{2x}x+D_{2zs}Z_{s}+D_{2\lambda}\lambda + D_{2s} &(eq4)\\
0 \leq Y \, \perp \, \lambda \geq 0&(\perp)\\
\end{array}\right)\]
$A_{2s}, B_{2s}$ and $D_{2s}$ are vectors.



%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "ace"
%%% End: 
